Implicit spatial model to krill Dynamic Population in Antarctic Peninsula, 48-1 SubArea. SS3 aplications

### 2024-04-04 Run_SS3_Krill_481.Rmd
add refs

The stock assesment model was configured using Stock Synthesis (SS3 hereafter)[SS3](https://vlab.noaa.gov/web/stock-synthesis) [@Methot2013] with the most updated version (V.3.30.21). SS3 is a structured age and size stock evaluation model, in the class of models called *"Integrated stock evaluation analysis model"*. SS3 has a stock population sub-model that simulates growth, maturity, fecundity, recruitment, movement, and mortality processes, and observation sub-models and expected values for different types of data. The model is coded in `C++` with estimation parameters enabled by automatic differentiation (ADMB) [@Fournier2012; @Methot2013]. The analysis of results and outputs uses R tools and the graphical interface of the *r4ss* library [@Taylor2019; @Winker2023].

@@

# r4ss::run(
#   dir = dir1,
#   exe = "ss_osx",
#   skipfinished = FALSE, # TRUE will skip running if Report.sso present
#   show_in_console = TRUE # change to true to watch the output go past
# )
```

@@

```{r eval=FALSE, message=F, include=FALSE}
SS_plots(base.model7, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

@@

# model2
tablebias1 <- SShcbias(retroSummary2,quant="SSB",verbose=F)
tablebias2 <- SShcbias(retroSummary2,quant="F",verbose=F)

kbl(tablebias1, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias2, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")
```

>>>>

The stock assesment model was configured using Stock Synthesis (SS3 hereafter)[SS3](https://vlab.noaa.gov/web/stock-synthesis) [@Methot2013; @methot2020stock] with the most updated version (V.3.30.21). SS3 is a structured age and size stock evaluation model, in the class of models called *"Integrated stock evaluation analysis model"*. SS3 has a stock population sub-model that simulates growth, maturity, fecundity, recruitment, movement, and mortality processes, and observation sub-models and expected values for different types of data. The model is coded in `C++` with estimation parameters enabled by automatic differentiation (ADMB) [@Fournier2012; @Methot2013]. The analysis of results and outputs uses R tools and the graphical interface of the *r4ss* library [@Taylor2019; @Winker2023].

@@

# r4ss::run(
#   dir = dir2,
#   exe = "ss_osx",
#   skipfinished = FALSE, # TRUE will skip running if Report.sso present
#   show_in_console = TRUE # change to true to watch the output go past
# )
```

@@

```{r eval=FALSE, message=F, include=FALSE}
SS_plots(base.model2, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

@@

# model2
tablebias7 <- SShcbias(retroSummary7,quant="SSB",verbose=F)
tablebias07 <- SShcbias(retroSummary7,quant="F",verbose=F)

kbl(tablebias7, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias7, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")
```
